Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-08-13 tex/sections/avm.tex

The Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}} Smart Contract Execution
Environment (AscEE) is an abstract execution environment for executing Argennon smarts contracts (a.k.a\ Argennon
applications) in a safe and secure environment. An Argennon application essentially is an HTTP server whose state is
kept in the Argennon blockchain and its logic is described using an Argennon Standard Representation (ASR).

>>>>

The Argennon Smart Contract Execution
Environment (AscEE) is an abstract execution environment for executing Argennon smarts contracts (a.k.a\ Argennon
applications) in a safe and secure environment. An Argennon application essentially is an HTTP server whose state is
kept in the Argennon blockchain and its logic is described using an Argennon Standard Representation (ASR).

### 2022-08-13 tex/sections/intro.tex

The most common use for blockchains is in financial applications. This gives a crucial importance to the
security of the consensus protocol used in a blockchain. Unfortunately, many currently used blockchains are
vulnerable to a certain type of consensus attack, known as the bribery attack. In a bribery attack, an adversary
tries to corrupt participants of a protocol by offering them money to make them violate the protocol.

@@

Although a fully decentralized blockchain based on the participation of every user looks appealing, it is not as perfect
as it might seem. A blockchain consensus protocol relies on a network of computers, not humans. Ordinary users use
simple and similar computer systems. That means, they all have similar vulnerabilities and weaknesses which could be
used by an adversary to catastrophically attack the consensus protocol. For example, if a malware, probably using a
common zero-day
vulnerability, has the ability to infect a large portion of normal personal computers, it could be used by an
adversary to control the majority of participants in the consensus protocol and compromise the security of the
blockchain.

@@

To overcome these difficulties, Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}}
uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected by users via the Argennon Decentralized Autonomous Governance System
(ADAGs). This committee usually\footnote{The election term and the number of committee members can be changed by the
ADAGs.} is elected for a one-year term, has five members, and is responsible for minting new
blocks of the blockchain.
Each minted block is required to get approved by its corresponding validator committee. Validator committees are very
large sets of validators including at least three percent of the maximum possible stake of the system. A block is
approved if it takes approval votes from at least \(2/3\) of the total stake of its validator committee.

@@

Centralized block generation brings some interesting features to the Argennon platform, such as flexible and lower
fees, off chain fee payment, optimistic instant transaction confirmation, and runoff protection.
However, it also increases the possibility of transaction censorship. In Argennon, this problem is addressed by a
special High Priority Transaction (HPT) protocol.

Each block of the Argennon blockchain contains a set of Computational Integrity (CI) statements and a commitment to
the final ledger state of the block. The CI set defines how the final ledger state of the block can be reached from
the state of its previous block via a set of intermediate states.
Each individual CI statement defines an ordered list of external requests\footnote{External requests in Argennon are
similar to transactions in older blockchains.} and determines the intermediate states before and after executing those
requests:
\[
    \tau_{(s_i,s_{i+1},\mathbb{R})} \coloneqq \text{``$s_{i+1}$ is the next state after executing external requests
        $\mathbb{R}$ on state $s_i$''}
\]
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements (STARK/SNARK) from the Argennon cloud. They can also receive the state of the previous
block (the required part of it) and proofs that show the received data is consistent with the previous block commitment.

Verifying a succinct proof can be exponentially faster than replaying the computation. Moreover, verifications of
different CI statements are independent and can be done in parallel. As a result, a validator can use multiple cores for
verifying CI statements of a \textbf{single} block and different validator committees can simultaneously and
independently verify \textbf{different} blocks.
In addition, proof generation of different CI statements similarly can be done in parallel. However, for parallel
proof generation, the state transition needs to be known in advance. That's why in Argennon, delegates do not try
to generate proofs and focus all their computational power on executing external requests and
generating the state transition as fast as possible.

@@

A PVC server in Argennon, is a conventional data server which uses its computational and
storage resources to help the Argennon network process transactions. This encourages the development
of conventional networking, storage and compute hardware, which can benefit all areas of information technology.

>>>>

The most common use for blockchains is in financial applications. This gives a crucial importance to the
security of the consensus protocol used in a blockchain. Unfortunately, many currently used blockchains are
vulnerable to a certain type of consensus attack, known as the bribery attack. In a bribery attack, an adversary
tries to corrupt participants of a protocol by offering them money and making them violate the protocol.

@@

Although a fully decentralized blockchain based on the participation of every user looks appealing, it is not as perfect
as it might seem. The consensus protocol of a blockchain relies on a network of computers, not humans. Ordinary users
use simple and similar computer systems. That means, they all have similar vulnerabilities and weaknesses which could be
used by an adversary to catastrophically attack the consensus protocol. For instance, if a malware, probably using a
common zero-day
vulnerability, has the ability to infect a large portion of normal personal computers, it could be used by an
adversary to control the majority of participants in the consensus protocol and compromise the security of the
blockchain.

@@

To overcome these difficulties, Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}}
uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected by users via the Argennon Decentralized Autonomous Governance system
(ADAGs). This committee usually\footnote{The election term and the number of committee members can be changed by the
ADAGs.} is elected for a one-year term, has five members, and is responsible for minting new
blocks of the Argennon blockchain.
Each minted block is required to get approved by its corresponding validator committee. Validator committees are very
large sets of validators including at least three percent of the maximum possible stake of the system. A block is
approved if it takes approval votes from at least \(2/3\) of the total stake of its validator committee.

@@

Centralized block generation brings some interesting features to the Argennon platform, such as flexible and lower
fees, off chain fee payment, optimistic instant transaction confirmation, and runoff protection.
However, it also increases the possibility of transaction censorship. In Argennon, this problem is addressed by a
special High Priority Request (HPR) protocol.

Each block of the Argennon blockchain contains a set of Computational Integrity (CI) statements and a commitment to
the final ledger state of the block. The CI set defines how the final ledger state of the block can be reached from
the state of its previous block via a set of intermediate states.
Each individual CI statement defines an ordered list of external requests\footnote{External requests in Argennon are
similar to transactions in older blockchains.} and determines the state before and after executing those requests:
\[
    \tau_{(s_i,s_{i+1},\mathbb{R})} \coloneqq \text{``$s_{i+1}$ is the next state after executing external requests
        $\mathbb{R}$ on state $s_i$''}
\]
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements (STARK/SNARK) from the Argennon cloud. They can also receive the state of the previous
block (the required part of it) and proofs that show the received data is consistent with the previous block commitment.

Verifying a succinct proof can be exponentially faster than replaying the computation. Moreover, verifications of
different CI statements are independent of each other and can be done in parallel. As a result, a validator can use
multiple cores for verifying CI statements of a \textbf{single} block and different validator committees can
simultaneously and
independently verify \textbf{different} blocks.
In addition, proof generation of different CI statements similarly can be done in parallel. However, for parallel
proof generation, the state transition needs to be known in advance. That's why in Argennon, delegates do not try
to generate proofs and focus all their computational power on executing external requests and
generating the state transition as fast as possible.

@@

A PVC server in Argennon, is a conventional data server which uses its computational and
storage resources to help the Argennon network process transactions. This encourages the development
of conventional networking, storage and compute hardware, which can benefit all areas of information technology.
This contrasts with the approach of some older blockchains that incentivized the development of a totally
useless technology of hash calculation.
